---
title: "Supplementary Files"
Date: 30-8-2017
output:
  html_document: default
  html_notebook: default
Author: Ignatius Pang
---

## Description

I want to create the supplementary tables for this manuscript. 

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath("..")) 
```


```{r}
library(RCy3)
library(plyr)
library(dplyr)
library(RODBC)
library(sqldf)
library(knitr) # required for the 'kable' function for printing pretty table in html

sessionInfo()
```

## Read helper functions 
```{r}

source_directory_common <- '/home/ignatius/PostDoc/2016/Triplet_Motifs/Source/Common/'
## Load the root base directory for the entire project
options <- commandArgs(trailingOnly = TRUE)
source( file.path( source_directory_common, "parameters_file.R") ) 

source( file.path ( source_directory_common, 'draw_triplet_motif_network_helper.R') ) 
source( file.path ( source_directory_common, 'count_triplet_motifs_helper.R'))

supplementary_data_directory <- file.path(results_directory, "Supplementary_Files" ) 
create_directory_if_not_exists(supplementary_data_directory)

```

## Global parameters
```{r}


## All interactions in the kinase substrate network must be greater than this score
sharifpoor_kinase_substrate_network_threshold <- 2.5


## Thresholds for the Costanzo genetic interaction network
## Stringent negative genetic interactions must have score less than this threshold
costanzo_stringent_negative_gi_score_threshold    <- -0.12

## Stringent negative genetic interactions must have p-value less than this threshold
costanzo_stringent_negative_gi_p_value_threshold  <-  0.05	

## Stringent negative genetic interactions must have absolute value of stanard deviation (std_dev) less than this threshold
costanzo_stringent_negative_gi_std_dev_threshold <- 0.08
```


## Read data tables 
```{r}
results_directory <- file.path(   local_base_directory, "Results" ) 

triplet_motifs_costanzo_2016 <- read.table ( file.path( data_directory, "triplet_motifs_costanzo_2016.txt"), 
											 header =TRUE , stringsAsFactors = FALSE)

if ( ! ( "oln_id_a" %in% colnames( triplet_motifs_costanzo_2016) ) ) {
	triplet_motifs_costanzo_2016 <- triplet_motifs_costanzo_2016 %>%
								dplyr::rename(  oln_id_a = node_a , oln_id_b =  node_b ,  oln_id_c = node_c  )
}

toxic_upon_overexpression <- read.table ( file.path( data_directory, "overexpressed_toxic_genes.txt"), header=TRUE , stringsAsFactors = FALSE)

essential_genes <- read.table ( file.path( data_directory, "essential_genes.txt"), header=TRUE, stringsAsFactors = FALSE)

cell_cycle_peak_times_of_orfs <- read.table ( file.path( data_directory, "periodically_expressed_genes.txt"), header=TRUE, stringsAsFactors = FALSE)

gene_names <- read.table ( file.path(data_directory, "gene_names_table.txt"), sep="\t", header=TRUE, stringsAsFactors = FALSE, 
						    na.strings="", quote="\"")


## Results from Spatial Analysis of Functional Enrichment (SAFE tool)

enriched_functions <- read.table ( file= file.path( results_directory, "SAFE/20161123/Triplet_Motifs/safe_exported_reports_20161123.txt-node_properties_annotation-highest.txt"), 
								   header=TRUE, stringsAsFactors = TRUE, 
						    na.strings="", quote="", sep="\t")

## Table list all triplets where the genetic interactions overlap with other types of interactions 
triplets_gi_overlapping_other_edges <- read.table( file.path(supplementary_data_directory, "triplets_with_overlapping_edges.tab"), 
										header=TRUE, sep="\t", stringsAsFactors = FALSE, quote="" )


## List of GO terms shared by all three proteins in the triplet 
## The tables need t be pre-computed by the script: "GO_terms/count_go_terms.R"
shared_go_terms_BP_per_triplet <- read.table( file.path(supplementary_data_directory, "shared_go_terms_BP_per_triplet.tab"), 
										header=TRUE, sep="\t", stringsAsFactors = FALSE, quote="" )
shared_go_terms_CC_per_triplet <- read.table( file.path(supplementary_data_directory, "shared_go_terms_CC_per_triplet.tab"), 
										header=TRUE, sep="\t", stringsAsFactors = FALSE, quote="" )
shared_go_terms_MF_per_triplet <- read.table( file.path(supplementary_data_directory, "shared_go_terms_MF_per_triplet.tab"), 
										header=TRUE, sep="\t", stringsAsFactors = FALSE, quote="" )

## List of phenotypes shared by all three proteins in the triplet 
## Phenotype data obtained from SGD.
## This table needs to be pre-computed by the script 'Phenotype/count_triplets_with_same_phenotype.R'
triplet_shared_phenotype <- read.table( file.path(supplementary_data_directory, "motif_and_phenotypes_detail.txt"), 
										header=TRUE, sep="\t", stringsAsFactors = FALSE, quote="" )




```

## Negative Genetic interactions 
```{r}

constanzo_stringet_2016_negative_genetic_interactions <- sqldf( paste(  "select distinct query_oln_id_edited as query_oln_id
														, gene_names_a.gene_name as query_gene_name
														, gene_names_a.description as query_gene_description
														, array_oln_id_edited as array_oln_id
														, gene_names_b.gene_name as array_gene_name
														, gene_names_b.description as array_gene_description
														, genetic_interaction_score
													 from filtered_costanzo_stringent_2016 gi
                                                          left join gene_names as gene_names_a
																on gi.query_oln_id_edited = gene_names_a.oln_id
                                                          left join gene_names as gene_names_b
																on gi.array_oln_id_edited = gene_names_b.oln_id
													 where genetic_interaction_score < ", costanzo_stringent_negative_gi_score_threshold, 
															" and p_value < ", costanzo_stringent_negative_gi_p_value_threshold, 
															" and abs(std_dev) < ", costanzo_stringent_negative_gi_std_dev_threshold , ";" ) )

write.table ( constanzo_stringet_2016_negative_genetic_interactions, 
			  file.path(supplementary_data_directory, "constanzo_stringet_2016_negative_genetic_interactions.tab"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )

kable(head( constanzo_stringet_2016_negative_genetic_interactions))
dim( constanzo_stringet_2016_negative_genetic_interactions)
```

## Protein interaction networks
```{r}


raw_sbi_interactome_joined <- sqldf(  " select gene_names_a.gene_name as gene_name_a
,oln_id_a
,gene_names_a.description as gene_description_a

,gene_names_b.gene_name as gene_name_b
,oln_id_b
,gene_names_b.description as gene_description_b

,pubmed_id
,expt_system
,source_table
,ppi.description
,author
			from raw_sbi_interactome ppi
					left join gene_names as gene_names_a
																on ppi.oln_id_a = gene_names_a.oln_id
                                                          left join gene_names as gene_names_b
																on ppi.oln_id_b = gene_names_b.oln_id;")

write.table ( raw_sbi_interactome_joined, 
			  file.path(supplementary_data_directory, "protein-protein_interactions.tab"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )


kable(head(raw_sbi_interactome_joined ))
dim( raw_sbi_interactome_joined)

```


## Kinase-substrate network
```{r}

kinase_network_filtered <- dplyr::filter( kinase_network, score > sharifpoor_kinase_substrate_network_threshold) %>%
							dplyr::select(-interaction_id) %>%
							dplyr::select(one_of ( c("kinase_gene_name", "kinase_oln_id", "target_gene_name", "target_oln_id", "score" )))

kinase_network_filtered <- sqldf( " select gene_names_a.gene_name as kinase_gene_name
									, kinase_oln_id         
									, gene_names_a.description as kinase_gene_description
									
									, gene_names_b.gene_name as target_gene_name
									, target_oln_id
									, gene_names_b.description as target_gene_description
									
									, score            
										from kinase_network_filtered kinase_substrate
										left join gene_names as gene_names_a 
														on kinase_substrate.kinase_oln_id = gene_names_a.oln_id
                                        left join gene_names as gene_names_b
														on kinase_substrate.target_oln_id = gene_names_b.oln_id;")

write.table ( kinase_network_filtered, file.path(supplementary_data_directory, "kinase-substrate_interactions.tab"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )	


kable(head(kinase_network_filtered))
dim(kinase_network_filtered)

```


## Transcriptional regulatory network
```{r}

tf_network_filtered <- dplyr::filter( tf_network, gene_expression_evidence + binding_evidence >= 2 | combinatorial_evidence >= 1 ) 

tf_network_filtered <- sqldf( " select gene_names_a.gene_name as regulator_gene_name
								, regulator_oln_id         
								, gene_names_a.description as regulator_gene_description
								
								, gene_names_b.gene_name as target_gene_name
								, target_oln_id
								, gene_names_b.description as target_gene_description
								
								, gene_expression_evidence 
								, binding_evidence         
								, combinatorial_evidence   
								, regulation_direction    
								, pubmed_id              
									from tf_network_filtered tf
									left join gene_names as gene_names_a 
												on tf.regulator_oln_id = gene_names_a.oln_id
                                    left join gene_names as gene_names_b
												on tf.target_oln_id = gene_names_b.oln_id;")

write.table ( tf_network_filtered, file.path(supplementary_data_directory, "transcription_factor-target_gene_interactions.tab"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )	

kable(head( tf_network_filtered))
dim( tf_network_filtered)

```

## Build phenotype master table 
```{r}

toxic_upon_overexpression <- toxic_upon_overexpression %>%
								dplyr::select ( one_of ( c( "oln_id"))) %>%
								dplyr::mutate ( overexpression_toxic = 1)

essential_genes <- essential_genes %>%
						dplyr::mutate ( essential = 1)


cell_cycle_peak_times_of_orfs <- cell_cycle_peak_times_of_orfs %>%
									dplyr::mutate ( periodically_expressed = 1)


essential_periodic_expression_toxic_overexpression <- toxic_upon_overexpression %>%
														full_join ( essential_genes ) %>% 
														full_join (  cell_cycle_peak_times_of_orfs ) 



essential_periodic_expression_toxic_overexpression [is.na( essential_periodic_expression_toxic_overexpression  ) ] <- 0


essential_periodic_expression_toxic_overexpression <- essential_periodic_expression_toxic_overexpression %>%
 														dplyr::group_by ( oln_id) %>%
 														dplyr::summarise( overexpression_toxic = sum( overexpression_toxic), 
 																   essential = sum( essential), 
 																   periodically_expressed = sum( periodically_expressed))


essential_periodic_expression_toxic_overexpression <- full_join ( essential_periodic_expression_toxic_overexpression, gene_names ) %>%
													  dplyr::mutate ( overexpression_toxic = ifelse(is.na(overexpression_toxic), 0, overexpression_toxic),
													  				  essential = ifelse(is.na(essential), 0, essential),
													  				  periodically_expressed = ifelse(is.na(periodically_expressed), 
													  				  								  0, periodically_expressed)
													  				)

write.table ( essential_periodic_expression_toxic_overexpression, 
			  file.path(supplementary_data_directory, "phenotype_table.tab"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )

kable(head( essential_periodic_expression_toxic_overexpression))
dim( essential_periodic_expression_toxic_overexpression)

```



## Paralogs and Ohnologs
```{r}

orthomcl_paralogs <- clean_graph_table  (orthomcl_paralogs,  "oln_id_a", "oln_id_b", directed=FALSE ) %>%
					 dplyr::mutate( type="paralog")

sgd_ohnologs 	  <- clean_graph_table  (sgd_paralogs,  "oln_id_a", "oln_id_b", directed=FALSE ) %>% # This table actually contain ohnologs
					 dplyr::mutate( type="ohnolog") 

all_paralogs_and_ohnologs <- dplyr::union ( orthomcl_paralogs, sgd_ohnologs) %>%
							 dplyr::arrange( type) %>%
							 dplyr::group_by( oln_id_a, oln_id_b) %>%
							 dplyr::summarise( type=paste( type, collapse=", ")) %>%
							 dplyr::arrange(oln_id_a, oln_id_b)

all_paralogs_and_ohnologs <- sqldf( " select gene_names_a.gene_name as gene_name_a
									, oln_id_a         
									, gene_names_a.description as gene_description_a
									
									, gene_names_b.gene_name as gene_name_b
									, oln_id_b
									, gene_names_b.description as gene_description_b
									
									, type            
										from all_paralogs_and_ohnologs 
										left join gene_names as gene_names_a 
														on all_paralogs_and_ohnologs.oln_id_a = gene_names_a.oln_id
                                        left join gene_names as gene_names_b
														on all_paralogs_and_ohnologs.oln_id_b = gene_names_b.oln_id;")

# all_paralogs_and_ohnologs %>%
# 	dplyr::filter( grepl(",", type) )

write.table ( all_paralogs_and_ohnologs, file.path(supplementary_data_directory, "all_paralogs_and_ohnologs.tab"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )	

kable(head(all_paralogs_and_ohnologs))
dim(all_paralogs_and_ohnologs)

```




## All interactions combined together  (part 1)
```{r}

# Cleaning transcription factor-target gene interactions
tf_network_collated <- tibble::as_tibble(tf_network) %>%
						clean_graph_table ( "regulator_oln_id", "target_oln_id", directed=TRUE) %>%
						collate_interactions_from_both_direction( "regulator_oln_id", "target_oln_id", 
																	   "transcription factor-target down", "transcription factor-target up",
																	   "td", "tu", 
																	   "oln_id_a", "oln_id_b", "interaction_type", "interaction_type_abbrev")

# Cleaning kinase-substrate interactions
kinase_network_subset <- subset(kinase_network, score > sharifpoor_kinase_substrate_network_threshold)

kinase_network_collated <- 	tibble::as_tibble(kinase_network_subset) %>%
     clean_graph_table ( "kinase_oln_id", "target_oln_id", directed=TRUE) %>%
	collate_interactions_from_both_direction( "kinase_oln_id", "target_oln_id", 
													 "kinase-substrate down", "kinase-substrate up",
													 "kd", "ku", 
													 "oln_id_a", "oln_id_b", "interaction_type", "interaction_type_abbrev") 



# Cleaning SBI interactome
sbi_interactome <-  dplyr::select ( raw_sbi_interactome, one_of(c("oln_id_a", "oln_id_b")) ) %>% 
					dplyr::distinct()

sbi_interactome_collated <-  tibble::as_tibble(sbi_interactome) %>%
								clean_graph_table ( "oln_id_a", "oln_id_b", directed=FALSE) %>%
								collate_interactions_from_both_direction(  "oln_id_a", "oln_id_b", 
																			 "protein-protein", "protein-protein",
																			 "p", "p", 
																			 "oln_id_a", "oln_id_b", "interaction_type", "interaction_type_abbrev") 

# Cleaning the negative genetic interactions network

costanzo_2016_stringent_gi_collated <-  filtered_costanzo_stringent_2016 %>% 
	dplyr:: filter ( genetic_interaction_score < costanzo_stringent_negative_gi_score_threshold & 
					 	p_value < costanzo_stringent_negative_gi_p_value_threshold & 
					 	abs ( std_dev ) < costanzo_stringent_negative_gi_std_dev_threshold) %>%
	tibble::as_tibble() %>%
	clean_graph_table ( "query_oln_id_edited", "array_oln_id_edited", directed=FALSE) %>%
	collate_interactions_from_both_direction(  "query_oln_id_edited", "array_oln_id_edited",
											   "negative genetic interaction", "negative genetic interaction",
											   "ng", "ng",
											   "oln_id_a", "oln_id_b", "interaction_type", "interaction_type_abbrev")


# All interactions combined together
interactions_combined <- dplyr::bind_rows(tf_network_collated, kinase_network_collated, sbi_interactome_collated, costanzo_2016_stringent_gi_collated)


interactions_combined <- sqldf( " select gene_names_a.gene_name as gene_name_a
									, oln_id_a
									, gene_names_a.description as gene_description_a
									
									, gene_names_b.gene_name as gene_name_b
									, oln_id_b
									, gene_names_b.description as gene_description_b
									
									, interaction_type
									, interaction_type_abbrev
								  from interactions_combined 
										left join gene_names as gene_names_a 
														on interactions_combined.oln_id_a = gene_names_a.oln_id
                                        left join gene_names as gene_names_b
														on interactions_combined.oln_id_b = gene_names_b.oln_id;")


kable(head(interactions_combined))
dim(interactions_combined)


```



## Get densely annotated triplets 
```{r}

densely_annotated_triplet_motif <- sqldf( "select data_a.gene_name as gene_name_a
, motifs.oln_id_a
, data_a.description as gene_description_a

, data_b.gene_name as gene_name_b
, motifs.oln_id_b
, data_b.description as gene_description_b

, data_c.gene_name as gene_name_c
, motifs.oln_id_c
, data_c.description as gene_description_c

, upper(motifs.type_ac) as type_of_interaction_a_to_c
, upper(motifs.type_bc) as type_of_interaction_b_to_c
, case when type_ac > type_bc then upper( type_ac || type_bc ) else upper( type_bc || type_ac ) end as type_of_motif
, case when data_a.essential = 1 and data_b.essential = 1 and data_c.essential = 1 then 1 else 0 end as all_proteins_essential
, case when data_a.periodically_expressed = 1 and data_b.periodically_expressed = 1 and data_c.periodically_expressed = 1 then 1 else 0 end as all_proteins_periodically_expressed
, case when data_a.overexpression_toxic = 1 and data_b.overexpression_toxic = 1 and data_c.overexpression_toxic = 1 then 1 else 0 end as all_proteins_toxic_upon_protein_expression

, data_a.essential as is_protein_a_essential
, data_a.periodically_expressed as is_protein_a_periodically_expressed
, data_a.overexpression_toxic as is_protein_a_toxic_upon_overexpression

, data_b.essential as is_protein_b_essential
, data_b.periodically_expressed as is_protein_b_periodically_expressed
, data_b.overexpression_toxic as is_protein_b_toxic_upon_overexpression

, data_c.essential as is_protein_c_essential
, data_c.periodically_expressed as is_protein_c_periodically_expressed
, data_c.overexpression_toxic as is_protein_c_toxic_upon_overexpression

from triplet_motifs_costanzo_2016  motifs
		left outer join essential_periodic_expression_toxic_overexpression data_a
			on data_a.oln_id = oln_id_a
		left outer join essential_periodic_expression_toxic_overexpression data_b
			on data_b.oln_id = oln_id_b
		left outer join essential_periodic_expression_toxic_overexpression data_c
			on data_c.oln_id = oln_id_c;
", stringsAsFactors=FALSE)


## Calculate the number of other triplets sharing this negative genetic interactions
num_of_overlapping_triplets_table <-  densely_annotated_triplet_motif %>%
								dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b", "oln_id_c", 
															"type_of_interaction_a_to_c", "type_of_interaction_b_to_c" ))) %>%
								dplyr::group_by( oln_id_a, oln_id_b) %>%
								# Remember that we need to minus one here to exclude itself from the count
								dplyr::summarise( num_of_other_triplets_sharing_this_genetic_interaction = n() - 1) %>% 
								dplyr::ungroup()


densely_annotated_triplet_motif <- sqldf( " select x.*
											, coalesce( overlap.P, 0) as P
											, coalesce( overlap.K1, 0) as K1
											, coalesce( overlap.K2, 0) as K2
											, coalesce( overlap.T1, 0) as T1	
											, coalesce( overlap.T2, 0) as T2
											, coalesce( repeated_gi.num_of_other_triplets_sharing_this_genetic_interaction, 0) 
                                   					as num_of_other_triplets_sharing_this_genetic_interaction
											, coalesce(w_bp.go_BP_count, 0 ) as num_go_BP_shared
											, w_bp.go_BP_intersect_abc
											, coalesce(w_cc.go_CC_count, 0 ) as num_go_CC_shared
											, w_cc.go_CC_intersect_abc
											, coalesce(w_mf.go_MF_count, 0 ) as num_go_MF_shared
											, w_mf.go_MF_intersect_abc
											, coalesce(y.num_phenotype_shared, 0) num_phenotype_shared
											, y.phenotype_intersect_abc
										    from densely_annotated_triplet_motif x
												 left join triplets_gi_overlapping_other_edges overlap 
												   on  x.oln_id_a = overlap.oln_id_a
														and x.oln_id_b = overlap.oln_id_b
														and x.oln_id_c = overlap.oln_id_c 
														and x.type_of_interaction_a_to_c = upper(overlap.type_ac)
														and x.type_of_interaction_b_to_c = upper(overlap.type_bc)
												 left join num_of_overlapping_triplets_table repeated_gi
													on x.oln_id_a = repeated_gi.oln_id_a
														and x.oln_id_b = repeated_gi.oln_id_b
												 left join shared_go_terms_BP_per_triplet  w_bp
										  			on  x.oln_id_a = w_bp.oln_id_a
														and x.oln_id_b = w_bp.oln_id_b
														and x.oln_id_c = w_bp.oln_id_c 
														and x.type_of_interaction_a_to_c = upper(w_bp.type_ac)
														and x.type_of_interaction_b_to_c = upper(w_bp.type_bc)
												 left join shared_go_terms_CC_per_triplet  w_cc
										  			on  x.oln_id_a = w_cc.oln_id_a
														and x.oln_id_b = w_cc.oln_id_b
														and x.oln_id_c = w_cc.oln_id_c 
														and x.type_of_interaction_a_to_c = upper(w_cc.type_ac)
														and x.type_of_interaction_b_to_c = upper(w_cc.type_bc)
												 left join shared_go_terms_MF_per_triplet  w_mf
										  			on  x.oln_id_a = w_mf.oln_id_a
														and x.oln_id_b = w_mf.oln_id_b
														and x.oln_id_c = w_mf.oln_id_c 
														and x.type_of_interaction_a_to_c = upper(w_mf.type_ac)
														and x.type_of_interaction_b_to_c = upper(w_mf.type_bc)
										  		 left join triplet_shared_phenotype y
										  			on  x.oln_id_a = y.oln_id_a
														and x.oln_id_b = y.oln_id_b
														and x.oln_id_c = y.oln_id_c 
														and x.type_of_interaction_a_to_c = upper(y.type_ac)
														and x.type_of_interaction_b_to_c = upper(y.type_bc)
														 ")

write.table ( densely_annotated_triplet_motif, file.path(supplementary_data_directory, "list_of_triplet_motifs.tab"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )

kable(head( densely_annotated_triplet_motif))
dim (densely_annotated_triplet_motif )
```


## Interactions that are part of triplets, excluding those that are not part of triplets
```{r}

gene_a <- as.character( as.vector(c( t(triplet_motifs_costanzo_2016[,1]) ,
									 t(triplet_motifs_costanzo_2016[,1])    , 
									 t(triplet_motifs_costanzo_2016[,2]) ) ))
	
gene_b <- as.character( as.vector(c( t(triplet_motifs_costanzo_2016[,2]) ,
									 t(triplet_motifs_costanzo_2016[,3])    , 
									 t(triplet_motifs_costanzo_2016[,3]) ) ))
	
edge_type_attributes <- as.character( as.vector( c( 
		rep( "ng", length(triplet_motifs_costanzo_2016[,1] )),
		t(triplet_motifs_costanzo_2016[, c("type_ac")]),
		t(triplet_motifs_costanzo_2016[, c("type_bc")])
	)  ) ) 
	
interactions_from_triplet_motifs <- data.frame( oln_id_a = gene_a, oln_id_b = gene_b, type_of_interaction = edge_type_attributes  )

interactions_from_triplet_motifs <- sqldf( " select gene_names_a.gene_name as gene_name_a
									, oln_id_a         
									, gene_names_a.description as gene_description_a
									
									, gene_names_b.gene_name as gene_name_b
									, oln_id_b
									, gene_names_b.description as gene_description_b
									
									, type_of_interaction            
										from interactions_from_triplet_motifs interactions 
										left join gene_names as gene_names_a 
														on interactions.oln_id_a = gene_names_a.oln_id
                                        left join gene_names as gene_names_b
														on interactions.oln_id_b = gene_names_b.oln_id;")

interactions_from_triplet_motifs <- interactions_from_triplet_motifs %>% dplyr::distinct()

write.table ( interactions_from_triplet_motifs, 
			  file.path(supplementary_data_directory, "interactions_from_triplet_motifs_only.tab"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )

kable(head( interactions_from_triplet_motifs))
dim( interactions_from_triplet_motifs)

```



## All interactions combined together  (part 2)
```{r}

interactions_from_triplet_motifs <- dplyr::mutate(interactions_from_triplet_motifs, is_part_of_a_triplet=1) %>%
									dplyr::rename( interaction_type_abbrev =type_of_interaction )

interactions_combined <- dplyr::left_join (interactions_combined, interactions_from_triplet_motifs,
										   by = c("gene_name_a", "oln_id_a", "gene_description_a", 
										   	      "gene_name_b", "oln_id_b", "gene_description_b", "interaction_type_abbrev")) 

interactions_combined <- dplyr::mutate( interactions_combined, is_part_of_a_triplet = ifelse( is.na(is_part_of_a_triplet), 0,1 ) )

write.table ( interactions_combined, file.path(supplementary_data_directory, "all_interactions.tab"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )	
```



