---
title: "R Notebook"
Date: 13-7-2016
output:
  html_document: default
  html_notebook: default
Author: Ignatius Pang
---

## Description
I want to visualize the network and draw network figures for the manuscript. 


```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath("..")) 
```


## Load libraires
```{r}
library(RCy3)
library(plyr)
library(dplyr)
library(sqldf)

sessionInfo()
```




## Read helper functions 
```{r}
# cd '/home/ignatius/PostDoc/2016/Triplet_Motifs/Source/Poster/'

## Load the root base directory for the entire project
options <- commandArgs(trailingOnly = TRUE)
# setwd( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Source")

source( file.path( getwd(), "Common/parameters_file.R") ) 

source( file.path ( source_directory_common, 'draw_triplet_motif_network_helper.R') ) 
source( file.path ( source_directory_common, 'count_triplet_motifs_helper.R'))

supplementary_data_directory <- file.path(results_directory, "Supplementary_Files" ) 
create_directory_if_not_exists(supplementary_data_directory)

list_of_triplets_directory <- '/home/ignatius/PostDoc/2016/Triplet_Motifs/Data/Triplet_Motifs_R_data'
```

## Read data tables 
```{r}
results_directory <- file.path(   local_base_directory, "Results" ) 
networks_directory <- file.path ( results_directory, "Figures/Networks")

triplet_motifs_costanzo_2016 <- read.table ( file.path( list_of_triplets_directory, "triplet_motifs_costanzo_2016.txt"), 
											 header =TRUE , stringsAsFactors = FALSE)

if ( ! ( "oln_id_a" %in% colnames( triplet_motifs_costanzo_2016) ) ) {
	triplet_motifs_costanzo_2016 <- triplet_motifs_costanzo_2016 %>%
								dplyr::rename(  oln_id_a = node_a , oln_id_b =  node_b ,  oln_id_c = node_c  )
}

toxic_upon_overexpression <- read.table ( file.path( data_directory, "overexpressed_toxic_genes.txt"), header=TRUE , stringsAsFactors = FALSE)

essential_genes <- read.table ( file.path( data_directory, "essential_genes.txt"), header=TRUE, stringsAsFactors = FALSE)

cell_cycle_peak_times_of_orfs <- read.table ( file.path( data_directory, "periodically_expressed_genes.txt"), header=TRUE, stringsAsFactors = FALSE)

gene_names <- read.table ( file.path(data_directory, "gene_names_table.txt"), sep="\t", header=TRUE, stringsAsFactors = FALSE, 
						    na.strings="", quote="\"")


## Results from Spatial Analysis of Functional Enrichment (SAFE tool)

enriched_functions <- read.table ( file= file.path( results_directory, "SAFE/20161123/Triplet_Motifs/safe_exported_reports_20161123.txt-node_properties_annotation-highest.txt"), 
								   header=TRUE, stringsAsFactors = TRUE, 
						    na.strings="", quote="", sep="\t")

```

## Build phenotype master table 
```{r}

toxic_upon_overexpression <- toxic_upon_overexpression %>%
								dplyr::select ( one_of ( c( "oln_id"))) %>%
								dplyr::mutate ( overexpression_toxic = 1)

essential_genes <- essential_genes %>%
						dplyr::mutate ( essential = 1)


cell_cycle_peak_times_of_orfs <- cell_cycle_peak_times_of_orfs %>%
									dplyr::mutate ( periodically_expressed = 1)


essential_periodic_expression_toxic_overexpression <- toxic_upon_overexpression %>%
														full_join ( essential_genes ) %>% 
														full_join (  cell_cycle_peak_times_of_orfs ) 



essential_periodic_expression_toxic_overexpression [is.na( essential_periodic_expression_toxic_overexpression  ) ] <- 0


essential_periodic_expression_toxic_overexpression <- essential_periodic_expression_toxic_overexpression %>%
 														dplyr::group_by ( oln_id) %>%
 														dplyr::summarise( overexpression_toxic = sum( overexpression_toxic), 
 																   essential = sum( essential), 
 																   periodically_expressed = sum( periodically_expressed))


write.table ( essential_periodic_expression_toxic_overexpression, 
			  file.path(supplementary_data_directory, "essential_periodic_expression_toxic_overexpression.txt"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )

```

## Get densely annotated triplets 
```{r}

densely_annotated_triplet_motif <- sqldf( "select motifs.* 
, data_a.essential as essential_a, data_a.periodically_expressed as periodically_expressed_a, data_a.overexpression_toxic as overexpression_toxic_a
, data_b.essential as essential_b, data_b.periodically_expressed as periodically_expressed_b, data_b.overexpression_toxic as overexpression_toxic_b
, data_c.essential as essential_c, data_c.periodically_expressed as periodically_expressed_c, data_c.overexpression_toxic as overexpression_toxic_c

, data_a.essential + data_b.essential + data_c.essential as essential_score
, data_a.periodically_expressed + data_b.periodically_expressed + data_c.periodically_expressed as periodically_expressed_score
, data_a.overexpression_toxic + data_b.overexpression_toxic + data_c.overexpression_toxic as overexpression_toxic_score

, case when data_a.essential = 1 and data_b.essential = 1 and data_c.essential = 1 then 1 else 0 end as essential_abc
, case when data_a.periodically_expressed = 1 and data_b.periodically_expressed = 1 and data_c.periodically_expressed = 1 then 1 else 0 end as periodically_expressed_abc
, case when data_a.overexpression_toxic = 1 and data_b.overexpression_toxic = 1 and data_c.overexpression_toxic = 1 then 1 else 0 end as overexpression_toxic_abc

, case when data_a.essential is not null then data_a.essential else 0 end 
+ case when data_a.periodically_expressed is not null then data_a.periodically_expressed else 0 end 
+ case when data_a.overexpression_toxic is not null then data_a.overexpression_toxic else 0 end 
+ case when data_b.essential is not null then data_b.essential else 0 end   
+ case when data_b.periodically_expressed  is not null then data_b.periodically_expressed else 0 end 
+ case when data_b.overexpression_toxic  is not null then data_b.overexpression_toxic else 0 end  as score_ab

, case when data_c.essential is not null then data_c.essential else 0 end 
+ case when data_c.periodically_expressed is not null then data_c.periodically_expressed else 0 end 
+ case when data_c.overexpression_toxic is not null then data_c.overexpression_toxic else 0 end as score_c

from triplet_motifs_costanzo_2016  motifs
		left outer join essential_periodic_expression_toxic_overexpression data_a
			on data_a.oln_id = oln_id_a
		left outer join essential_periodic_expression_toxic_overexpression data_b
			on data_b.oln_id = oln_id_b
		left outer join essential_periodic_expression_toxic_overexpression data_c
			on data_c.oln_id = oln_id_c;
", stringsAsFactors=FALSE)


write.table ( densely_annotated_triplet_motif, file.path(supplementary_data_directory, "densely_annotated_triplet_motif.txt"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )


```


## Figure 5c. A genetic interaction overlapping with multiple triplets. Focus on protein complexes. 
```{r}

list_of_gi <- count_repeated_gi_in_triplet_motifs_look_at_gi( triplet_motifs_costanzo_2016 ) %>%
			  dplyr::filter( motif_type != "others") %>%
			  dplyr::filter (motif_type == 'protein_complexes') %>%
			  dplyr::filter ( counts == '4') %>%
			  # TIM complex YHR083W, YGR082W	  
			  dplyr::filter ( (oln_id_a == 'YHR083W' & oln_id_b == 'YGR082W') |
			  				  (oln_id_a == 'YGR082W' & oln_id_b == 'YHR083W')  )

selected_regulatory_triplets <- triplet_motifs_costanzo_2016 %>%
	dplyr::right_join ( list_of_gi) %>%
	dplyr::filter(	type_ac == 'p'  & type_bc == 'p' )  %>%
	dplyr::select ( one_of( c( "oln_id_a", "oln_id_b", "oln_id_c", "type_ac", "type_bc", "genetic_interaction_score" ))) %>%
	as.data.frame()

cw <- draw_triplet_motif_network  ( selected_regulatory_triplets, 'Tightly regulated proteins' ) 

cw <- add_node_attributes(cw, gene_names , "oln_id")

cw <- add_node_attributes ( cw, enriched_functions, "Node.label.ORF")

displayGraph(cw)
	
triplet_motif_network_display_style(cw) 

redraw (cw)

current_example_dir <- file.path( networks_directory, "Repeated_GI_Example")

create_directory_if_not_exists( current_example_dir) 

## saveNetwork command currently not working for unknown reasons
Sys.sleep(5)
saveImage ( cw, file.name= file.path( current_example_dir, "repeated_gi_example_protein_complexes"), image.type='pdf')

```

## Figure 5d. A genetic interaction overlapping with multiple triplets. Focus on regulatory triplets. 
```{r}

regulatory_triplets_overlapping_gi  <- function( num_triplets_overlapping) {
	list_of_gi <- count_repeated_gi_in_triplet_motifs_look_at_gi( triplet_motifs_costanzo_2016 ) %>%
			  dplyr::filter( motif_type != "others") %>%
			  dplyr::filter (motif_type == 'regulatory_triplets') %>%
			  dplyr::filter ( counts == '4') %>%
			  dplyr::filter ( (oln_id_a == 'YPL018W' & oln_id_b == 'YPL253C') | 
			  				  (oln_id_a == 'YPL253C' & oln_id_b == 'YPL018W')  	)


selected_regulatory_triplets <- triplet_motifs_costanzo_2016 %>%
	dplyr::right_join ( list_of_gi) %>%
	dplyr::filter(	( type_ac == 'tu'  & type_bc == 'tu') |
				   	( type_ac == 'td' & type_bc == 'p') |
				   	( type_ac == 'p' & type_bc == 'td') 
				    )  %>%
	dplyr::select ( one_of( c( "oln_id_a", "oln_id_b", "oln_id_c", "type_ac", "type_bc", "genetic_interaction_score" ))) %>%
	as.data.frame()

cw <- draw_triplet_motif_network  ( selected_regulatory_triplets, 'Tightly regulated proteins' ) 

cw <- add_node_attributes(cw, gene_names , "oln_id")

cw <- add_node_attributes ( cw, enriched_functions, "Node.label.ORF")

displayGraph(cw)
	
triplet_motif_network_display_style(cw) 

redraw (cw)

current_example_dir <- file.path( networks_directory, "Repeated_GI_Example")

create_directory_if_not_exists( current_example_dir) 

## saveNetwork command currently not working for unknown reasons
Sys.sleep(5)
saveImage ( cw, file.name= file.path( current_example_dir, 
									  paste("regulatory_", num_triplets_overlapping, "_triplets_overlapping_gi", sep="") ), 
									  image.type='pdf' )

	
}


# walk( 2:18, regulatory_triplets_overlapping_gi)

walk( 4, regulatory_triplets_overlapping_gi)


```


## Figure 5e. A genetic interaction overlapping with multiple triplets. Focus on signaling triplets. 
```{r}
signaling_triplets_overlapping_gi  <- function( num_triplets_overlapping) {

list_of_gi <- count_repeated_gi_in_triplet_motifs_look_at_gi( triplet_motifs_costanzo_2016 ) %>%
			  dplyr::filter( motif_type != "others") %>%
			  dplyr::filter (motif_type == 'signaling_triplets') %>%
			  dplyr::filter ( counts == '5') %>%
			  dplyr::filter ( (oln_id_a == 'YGR188C' & oln_id_b == 'YDL028C') | 
			  				  (oln_id_a == 'YDL028C' & oln_id_b == 'YGR188C')  	)


selected_regulatory_triplets <- triplet_motifs_costanzo_2016 %>%
	dplyr::right_join ( list_of_gi) %>%
	dplyr::filter(	( type_ac == 'ku'  & type_bc == 'ku') |
				   	( type_ac == 'kd' & type_bc == 'p') |
				   	( type_ac == 'p' & type_bc == 'kd') |
				   	( type_ac == 'ku' & type_bc == 'p') |
				   	( type_ac == 'p' & type_bc == 'ku') 
				    )  %>%
	dplyr::select ( one_of( c( "oln_id_a", "oln_id_b", "oln_id_c", "type_ac", "type_bc", "genetic_interaction_score" ))) %>%
	as.data.frame()

cw <- draw_triplet_motif_network  ( selected_regulatory_triplets, 'Tightly regulated proteins' ) 

cw <- add_node_attributes(cw, gene_names , "oln_id")

cw <- add_node_attributes ( cw, enriched_functions, "Node.label.ORF")

displayGraph(cw)
	
triplet_motif_network_display_style(cw) 

redraw (cw)

current_example_dir <- file.path( networks_directory, "Repeated_GI_Example")

create_directory_if_not_exists( current_example_dir) 

## saveNetwork command currently not working for unknown reasons
Sys.sleep(5)
saveImage ( cw, file.name= file.path( current_example_dir, 
									  paste( "signaling_", num_triplets_overlapping, "_triplets_overlapping_gi", sep="") ), 
			image.type='pdf')

}

#walk( 2:16, signaling_triplets_overlapping_gi)

walk( 5, signaling_triplets_overlapping_gi)


```

## Figure 7. Triplet motifs consisting of proteins that are essential, toxic upon protein overexpression and those periodically expressed in the cell cycle. 

## Figure 7a. Venn Diagram

```{r}

results_phenotypic_annotation_enriched_motif <- sqldf( "select distinct oln_id_a, oln_id_b, oln_id_c
	, case when essential_a = 1 and essential_b = 1 and essential_c = 1 then 1 else 0 end as essential_abc
	, case when periodically_expressed_a = 1 and periodically_expressed_b = 1 and periodically_expressed_c = 1 then 1 else 0 end as periodically_expressed_abc
	, case when overexpression_toxic_a = 1 and overexpression_toxic_b = 1 and overexpression_toxic_c = 1 then 1 else 0 end as overexpression_toxic_abc
from densely_annotated_triplet_motif

where ( ( type_ac = 'p' and type_bc = 'p' )
	or  ( type_ac = 'tu' and type_bc = 'tu' ) 
	or  ( type_ac = 'ku' and type_bc = 'ku' ) 
	or  ( type_ac = 'p'  and type_bc = 'ku' ) 
	or  ( type_ac = 'p'  and type_bc = 'td' ) 
	or  ( type_ac = 'p'  and type_bc = 'kd' ) 
	or  ( type_ac = 'ku' and type_bc = 'p'  ) 
	or  ( type_ac = 'td' and type_bc = 'p'  ) 
	or  ( type_ac = 'kd' and type_bc = 'p'  )
      )  ;" ) 
      
      
      
counts_for_venn_diagram <- sqldf( "select essential_abc, periodically_expressed_abc, overexpression_toxic_abc, count(*) as counts
from results_phenotypic_annotation_enriched_motif
group by essential_abc, periodically_expressed_abc, overexpression_toxic_abc; "  )


print ( counts_for_venn_diagram)
      
```



## Figure 7b. Network of tightly regulated proteins (involved in spindle pole formation)
```{r}
triplet_motifs_costanzo <- sqldf( "select oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
from densely_annotated_triplet_motif
where ( ( type_ac = 'p' and type_bc = 'p' )
	or  ( type_ac = 'tu' and type_bc = 'tu' ) 
	or  ( type_ac = 'ku' and type_bc = 'ku' ) 
	or  ( type_ac = 'p' and type_bc = 'ku' ) 
	or  ( type_ac = 'p' and type_bc = 'td' ) 
	or  ( type_ac = 'p' and type_bc = 'kd' ) 
	or  ( type_ac = 'ku' and type_bc = 'p' ) 
	or  ( type_ac = 'td' and type_bc = 'p' ) 
	or  ( type_ac = 'kd' and type_bc = 'p' ) 	
      ) 
	  and score_ab >=6
	  and score_c >=3 ;", stringsAsFactors=FALSE)

triplet_motifs_costanzo <- as.data.frame ( triplet_motifs_costanzo )

cw <- draw_triplet_motif_network  ( triplet_motifs_costanzo, 'Tightly regulated proteins' ) 

cw <- add_node_attributes(cw, gene_names , "oln_id")

cw <- add_node_attributes ( cw, enriched_functions, "Node.label.ORF")

displayGraph(cw)
	
triplet_motif_network_display_style(cw) 

redraw (cw)

current_example_dir <- file.path( networks_directory, "Achilles_heel/Spindle-pole body example")

create_directory_if_not_exists( current_example_dir) 

## saveNetwork command currently not working for unknown reasons
#saveNetwork(cw, file.name= file.path( current_example_dir, "spindle-pole body example"), format='cys')

saveImage ( cw, file.name= file.path( current_example_dir, "spindle-pole body example"), image.type='pdf')

```



## Figure 7c. Triplets in which all proteins are essential and their corresponding genes are expressed periodically in the cell cycle. 
```{r}

triplet_motifs_costanzo <- sqldf( "select distinct oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
from densely_annotated_triplet_motif
where ( ( type_ac = 'p'  and type_bc = 'p' )
	or  ( type_ac = 'tu' and type_bc = 'tu' ) 
	or  ( type_ac = 'ku' and type_bc = 'ku' ) 
	or  ( type_ac = 'p'  and type_bc = 'ku' ) 
	or  ( type_ac = 'p'  and type_bc = 'td' ) 
	or  ( type_ac = 'p'  and type_bc = 'kd' ) 
	or  ( type_ac = 'ku' and type_bc = 'p' ) 
	or  ( type_ac = 'td' and type_bc = 'p' ) 
	or  ( type_ac = 'kd' and type_bc = 'p' ) 	
      ) 
	  and essential_a = 1
	  and essential_b = 1
	  and essential_c = 1


	  and periodically_expressed_a = 1
	  and periodically_expressed_b = 1
	  and periodically_expressed_c = 1


except 

select oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
from densely_annotated_triplet_motif
where ( ( type_ac = 'p' and type_bc = 'p' )
	or  ( type_ac = 'tu' and type_bc = 'tu' ) 
	or  ( type_ac = 'ku' and type_bc = 'ku' ) 
	or  ( type_ac = 'p' and type_bc = 'ku' ) 
	or  ( type_ac = 'p' and type_bc = 'td' ) 
	or  ( type_ac = 'p' and type_bc = 'kd' ) 
	or  ( type_ac = 'ku' and type_bc = 'p' ) 
	or  ( type_ac = 'td' and type_bc = 'p' ) 
	or  ( type_ac = 'kd' and type_bc = 'p' ) 	
      ) 
	  and score_ab >=6;", stringsAsFactors=FALSE)

triplet_motifs_costanzo <- as.data.frame ( triplet_motifs_costanzo )

cw <- draw_triplet_motif_network  ( triplet_motifs_costanzo, 'essential periodically expressed' ) 

cw <- add_node_attributes(cw, gene_names , "oln_id")

cw <- add_node_attributes ( cw, enriched_functions, "Node.label.ORF")

displayGraph(cw)
	
triplet_motif_network_display_style(cw) 

redraw (cw)

current_example_dir <- file.path( networks_directory, "Achilles_heel/Essential and periodically expressed")

create_directory_if_not_exists( current_example_dir) 

saveImage ( cw, file.name= file.path( current_example_dir, "essential and periodically expressed"), image.type='pdf')

```



## Figure 7d. Triplets where all proteins are essential and toxic upon overexpression. 
```{r}

triplet_motifs_costanzo <- sqldf( "select distinct oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
from densely_annotated_triplet_motif
where ( ( type_ac = 'p' and type_bc = 'p' )
	or  ( type_ac = 'tu' and type_bc = 'tu' ) 
	or  ( type_ac = 'ku' and type_bc = 'ku' ) 
	or  ( type_ac = 'p' and type_bc = 'ku' ) 
	or  ( type_ac = 'p' and type_bc = 'td' ) 
	or  ( type_ac = 'p' and type_bc = 'kd' ) 
	or  ( type_ac = 'ku' and type_bc = 'p' ) 
	or  ( type_ac = 'td' and type_bc = 'p' ) 
	or  ( type_ac = 'kd' and type_bc = 'p' ) 	
      ) 
	  and essential_a = 1
	  and essential_b = 1
	  and essential_c = 1

	  and overexpression_toxic_a = 1
	  and overexpression_toxic_b = 1
	  and overexpression_toxic_c = 1
									
except 

select oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
from densely_annotated_triplet_motif
where ( ( type_ac = 'p'  and type_bc = 'p' )
	or  ( type_ac = 'tu' and type_bc = 'tu' ) 
	or  ( type_ac = 'ku' and type_bc = 'ku' ) 
	or  ( type_ac = 'p'  and type_bc = 'ku' ) 
	or  ( type_ac = 'p'  and type_bc = 'td' ) 
	or  ( type_ac = 'p'  and type_bc = 'kd' ) 
	or  ( type_ac = 'ku' and type_bc = 'p' ) 
	or  ( type_ac = 'td' and type_bc = 'p' ) 
	or  ( type_ac = 'kd' and type_bc = 'p' ) 	
      ) 
	  and score_ab >=6;", stringsAsFactors=FALSE)

triplet_motifs_costanzo <- as.data.frame ( triplet_motifs_costanzo )

cw <- draw_triplet_motif_network  ( triplet_motifs_costanzo, 'essential overexpression' ) 

cw <- add_node_attributes(cw, gene_names , "oln_id")

cw <- add_node_attributes ( cw, enriched_functions, "Node.label.ORF")

displayGraph(cw)

triplet_motif_network_display_style(cw) 

redraw (cw)

current_example_dir <- file.path( networks_directory, "Achilles_heel/Essential and toxic upon overexpression")

create_directory_if_not_exists( current_example_dir) 

saveImage ( cw, file.name= file.path( current_example_dir, "Essential and toxic upon overexpression"), image.type='pdf')

```


## Figure 7e. All three genes in the triplet motif are cell cycle-regulated and the corresponding protein product is toxic upon overexpression. 
```{r}

triplet_motifs_costanzo <- sqldf( "select distinct oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
									from densely_annotated_triplet_motif
									where ( ( type_ac = 'p' and type_bc = 'p' )
									or  ( type_ac = 'tu' and type_bc = 'tu' ) 
									or  ( type_ac = 'ku' and type_bc = 'ku' ) 
									or  ( type_ac = 'p' and type_bc = 'ku' ) 
									or  ( type_ac = 'p' and type_bc = 'td' ) 
									or  ( type_ac = 'p' and type_bc = 'kd' ) 
									or  ( type_ac = 'ku' and type_bc = 'p' ) 
									or  ( type_ac = 'td' and type_bc = 'p' ) 
									or  ( type_ac = 'kd' and type_bc = 'p' ) 	
									) 
									and periodically_expressed_a = 1
									and periodically_expressed_b = 1
									and periodically_expressed_c = 1

									
									and overexpression_toxic_a = 1
									and overexpression_toxic_b = 1
									and overexpression_toxic_c = 1

									except 
									
									select oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
									from densely_annotated_triplet_motif
									where ( ( type_ac = 'p' and type_bc = 'p' )
									or  ( type_ac = 'tu' and type_bc = 'tu' ) 
									or  ( type_ac = 'ku' and type_bc = 'ku' ) 
									or  ( type_ac = 'p' and type_bc = 'ku' ) 
									or  ( type_ac = 'p' and type_bc = 'td' ) 
									or  ( type_ac = 'p' and type_bc = 'kd' ) 
									or  ( type_ac = 'ku' and type_bc = 'p' ) 
									or  ( type_ac = 'td' and type_bc = 'p' ) 
									or  ( type_ac = 'kd' and type_bc = 'p' ) 	
									) 
									and score_ab >=6;", stringsAsFactors=FALSE)

triplet_motifs_costanzo <- as.data.frame ( triplet_motifs_costanzo )

cw <- draw_triplet_motif_network  ( triplet_motifs_costanzo, 'periodically expressed and toxic upon overexpression' ) 

cw <- add_node_attributes(cw, gene_names , "oln_id")

cw <- add_node_attributes ( cw, enriched_functions, "Node.label.ORF")

displayGraph(cw)

triplet_motif_network_display_style(cw) 

redraw (cw)

current_example_dir <- file.path( networks_directory, "Achilles_heel/Periodically expressed and toxic upon overexpression")

create_directory_if_not_exists( current_example_dir) 

saveImage ( cw, file.name= file.path( current_example_dir, "Periodically expressed and toxic upon overexpression"),
			image.type='pdf')

```
