---
title: "R Notebook"
Date: 13-7-2016
output:
  html_document: default
  html_notebook: default
Author: Ignatius Pang
---

Description: I want to visualize the network, which consists of all the triplet motifs. Only edges in triplet motifs are shown.


```{r}
library(RCy3)
library(dplyr)
library(RODBC)
library(sqldf)
```




Read helper functions 
```{r}
# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Poster/'

## Load the root base directory for the entire project
options <- commandArgs(trailingOnly = TRUE)
source( "./Common/parameters_file.R")

setwd ( file.path( base_directory, 'Source/Figures') ) 

source( file.path ( source_directory_common, 'draw_triplet_motif_network_helper.R') ) 

```

Read data tables 
```{r}
triplet_motifs_costanzo_2016 <- read.table ( file.path( list_of_triplets_directory, "triplet_motifs_costanzo_2016.txt"), 
											 header =TRUE , stringsAsFactors = FALSE)

triplet_motifs_costanzo_2016 <- triplet_motifs_costanzo_2016 %>% 
								dplyr::rename( oln_id_a = node_a, oln_id_b = node_b, oln_id_c = node_c)

toxic_upon_overexpression <- read.table ( file.path( data_directory, "overexpressed_toxic_genes.txt"), header=TRUE , stringsAsFactors = FALSE)

essential_genes <- read.table ( file.path( data_directory, "essential_genes.txt"), header=TRUE, stringsAsFactors = FALSE)

cell_cycle_peak_times_of_orfs <- read.table ( file.path( data_directory, "periodically_expressed_genes.txt"), header=TRUE, stringsAsFactors = FALSE)

gene_names <- read.table ( file.path(data_directory, "gene_names_table.txt"), sep="\t", header=TRUE, stringsAsFactors = FALSE, 
						    na.strings="", quote="")


## Results from Spatial Analysis of Functional Enrichment (SAFE tool)

enriched_functions <- read.table ( file.path( results_directory, "SAFE/safe_exported_reports_20161123.txt-node_properties_annotation-highest.txt"), sep="\t", header=TRUE, stringsAsFactors = FALSE, 
						    na.strings="", quote="")

```

Build phenotype master table 
```{r}

toxic_upon_overexpression <- toxic_upon_overexpression %>%
								dplyr::select ( one_of ( c( "oln_id"))) %>%
								dplyr::mutate ( overexpression_toxic = 1)

essential_genes <- essential_genes %>%
						dplyr::mutate ( essential = 1)


cell_cycle_peak_times_of_orfs <- cell_cycle_peak_times_of_orfs %>%
									dplyr::mutate ( periodically_expressed = 1)


essential_periodic_expression_toxic_overexpression <- toxic_upon_overexpression %>%
														full_join ( essential_genes ) %>% 
														full_join (  cell_cycle_peak_times_of_orfs ) 



essential_periodic_expression_toxic_overexpression [is.na( essential_periodic_expression_toxic_overexpression  ) ] <- 0


essential_periodic_expression_toxic_overexpression <- essential_periodic_expression_toxic_overexpression %>%
 														group_by ( oln_id) %>%
 														summarise( overexpression_toxic = sum( overexpression_toxic), 
 																   essential = sum( essential), 
 																   periodically_expressed = sum( periodically_expressed))

```

Get densely annotated triplets 
```{r}

densely_annotated_triplet_motif <- sqldf( "select motifs.* 
, data_a.essential as essential_a, data_a.periodically_expressed as periodically_expressed_a, data_a.overexpression_toxic as overexpression_toxic_a
, data_b.essential as essential_b, data_b.periodically_expressed as periodically_expressed_b, data_b.overexpression_toxic as overexpression_toxic_b
, data_c.essential as essential_c, data_c.periodically_expressed as periodically_expressed_c, data_c.overexpression_toxic as overexpression_toxic_c

, data_a.essential + data_b.essential + data_c.essential as essential_score
, data_a.periodically_expressed + data_b.periodically_expressed + data_c.periodically_expressed as periodically_expressed_score
, data_a.overexpression_toxic + data_b.overexpression_toxic + data_c.overexpression_toxic as overexpression_toxic_score

, case when data_a.essential = 1 and data_b.essential = 1 and data_c.essential = 1 then 1 else 0 end as essential_abc
, case when data_a.periodically_expressed = 1 and data_b.periodically_expressed = 1 and data_c.periodically_expressed = 1 then 1 else 0 end as periodically_expressed_abc
, case when data_a.overexpression_toxic = 1 and data_b.overexpression_toxic = 1 and data_c.overexpression_toxic = 1 then 1 else 0 end as overexpression_toxic_abc

, case when data_a.essential is not null then data_a.essential else 0 end 
+ case when data_a.periodically_expressed is not null then data_a.periodically_expressed else 0 end 
+ case when data_a.overexpression_toxic is not null then data_a.overexpression_toxic else 0 end 
+ case when data_b.essential is not null then data_b.essential else 0 end   
+ case when data_b.periodically_expressed  is not null then data_b.periodically_expressed else 0 end 
+ case when data_b.overexpression_toxic  is not null then data_b.overexpression_toxic else 0 end  as score_ab

, case when data_c.essential is not null then data_c.essential else 0 end 
+ case when data_c.periodically_expressed is not null then data_c.periodically_expressed else 0 end 
+ case when data_c.overexpression_toxic is not null then data_c.overexpression_toxic else 0 end as score_c

from triplet_motifs_costanzo_2016  motifs
		left outer join essential_periodic_expression_toxic_overexpression data_a
			on data_a.oln_id = oln_id_a
		left outer join essential_periodic_expression_toxic_overexpression data_b
			on data_b.oln_id = oln_id_b
		left outer join essential_periodic_expression_toxic_overexpression data_c
			on data_c.oln_id = oln_id_c;
", stringsAsFactors=FALSE)


```



Network of tightly regulated proteins (involved in spindle pole formation)
```{r}
triplet_motifs_costanzo <- sqldf( "select oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
from densely_annotated_triplet_motif
where ( ( type_ac = 'p' and type_bc = 'p' )
	or  ( type_ac = 'tu' and type_bc = 'tu' ) 
	or  ( type_ac = 'ku' and type_bc = 'ku' ) 
	or  ( type_ac = 'p' and type_bc = 'ku' ) 
	or  ( type_ac = 'p' and type_bc = 'td' ) 
	or  ( type_ac = 'p' and type_bc = 'kd' ) 
	or  ( type_ac = 'ku' and type_bc = 'p' ) 
	or  ( type_ac = 'td' and type_bc = 'p' ) 
	or  ( type_ac = 'kd' and type_bc = 'p' ) 	
      ) 
	  and score_ab >=6
	  and score_c >=3 ;", stringsAsFactors=FALSE)

triplet_motifs_costanzo <- as.data.frame ( triplet_motifs_costanzo )

cw <- draw_triplet_motif_network  ( triplet_motifs_costanzo, 'Tightly regulated proteins' ) 

cw <- add_node_attributes(cw, gene_names , "oln_id")

cw <- add_node_attributes ( cw, enriched_functions, "Node.label.ORF")

displayGraph(cw)
	
triplet_motif_network_display_style(cw) 

redraw (cw)

current_example_dir <- file.path( results_directory, "Achilles_heel/Spindle-pole body example")

create_directory_if_not_exists( current_example_dir) 

## saveNetwork command currently not working for unknown reasons
#saveNetwork(cw, file.name= file.path( current_example_dir, "spindle-pole body example"), format='cys')

saveImage ( cw, file.name= file.path( current_example_dir, "spindle-pole body example"), image.type='pdf')

```

All three proteins in the motif needs to be essential and periodically expressed 
```{r}

triplet_motifs_costanzo <- sqldf( "select distinct oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
from densely_annotated_triplet_motif
where ( ( type_ac = 'p'  and type_bc = 'p' )
	or  ( type_ac = 'tu' and type_bc = 'tu' ) 
	or  ( type_ac = 'ku' and type_bc = 'ku' ) 
	or  ( type_ac = 'p'  and type_bc = 'ku' ) 
	or  ( type_ac = 'p'  and type_bc = 'td' ) 
	or  ( type_ac = 'p'  and type_bc = 'kd' ) 
	or  ( type_ac = 'ku' and type_bc = 'p' ) 
	or  ( type_ac = 'td' and type_bc = 'p' ) 
	or  ( type_ac = 'kd' and type_bc = 'p' ) 	
      ) 
	  and essential_a = 1
	  and essential_b = 1
	  and essential_c = 1


	  and periodically_expressed_a = 1
	  and periodically_expressed_b = 1
	  and periodically_expressed_c = 1


except 

select oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
from densely_annotated_triplet_motif
where ( ( type_ac = 'p' and type_bc = 'p' )
	or  ( type_ac = 'tu' and type_bc = 'tu' ) 
	or  ( type_ac = 'ku' and type_bc = 'ku' ) 
	or  ( type_ac = 'p' and type_bc = 'ku' ) 
	or  ( type_ac = 'p' and type_bc = 'td' ) 
	or  ( type_ac = 'p' and type_bc = 'kd' ) 
	or  ( type_ac = 'ku' and type_bc = 'p' ) 
	or  ( type_ac = 'td' and type_bc = 'p' ) 
	or  ( type_ac = 'kd' and type_bc = 'p' ) 	
      ) 
	  and score_ab >=6;", stringsAsFactors=FALSE)

triplet_motifs_costanzo <- as.data.frame ( triplet_motifs_costanzo )

cw <- draw_triplet_motif_network  ( triplet_motifs_costanzo, 'essential periodically expressed' ) 

cw <- add_node_attributes(cw, gene_names , "oln_id")

cw <- add_node_attributes ( cw, enriched_functions, "Node.label.ORF")

displayGraph(cw)
	
triplet_motif_network_display_style(cw) 

redraw (cw)

current_example_dir <- file.path( results_directory, "Achilles_heel/Essential and periodically expressed")

create_directory_if_not_exists( current_example_dir) 

saveImage ( cw, file.name= file.path( current_example_dir, "essential and periodically expressed"), image.type='pdf')

```


Essential and toxic upon overexpression
```{r}

triplet_motifs_costanzo <- sqldf( "select distinct oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
from densely_annotated_triplet_motif
where ( ( type_ac = 'p' and type_bc = 'p' )
	or  ( type_ac = 'tu' and type_bc = 'tu' ) 
	or  ( type_ac = 'ku' and type_bc = 'ku' ) 
	or  ( type_ac = 'p' and type_bc = 'ku' ) 
	or  ( type_ac = 'p' and type_bc = 'td' ) 
	or  ( type_ac = 'p' and type_bc = 'kd' ) 
	or  ( type_ac = 'ku' and type_bc = 'p' ) 
	or  ( type_ac = 'td' and type_bc = 'p' ) 
	or  ( type_ac = 'kd' and type_bc = 'p' ) 	
      ) 
	  and essential_a = 1
	  and essential_b = 1
	  and essential_c = 1

	  and overexpression_toxic_a = 1
	  and overexpression_toxic_b = 1
	  and overexpression_toxic_c = 1
									
except 

select oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
from densely_annotated_triplet_motif
where ( ( type_ac = 'p'  and type_bc = 'p' )
	or  ( type_ac = 'tu' and type_bc = 'tu' ) 
	or  ( type_ac = 'ku' and type_bc = 'ku' ) 
	or  ( type_ac = 'p'  and type_bc = 'ku' ) 
	or  ( type_ac = 'p'  and type_bc = 'td' ) 
	or  ( type_ac = 'p'  and type_bc = 'kd' ) 
	or  ( type_ac = 'ku' and type_bc = 'p' ) 
	or  ( type_ac = 'td' and type_bc = 'p' ) 
	or  ( type_ac = 'kd' and type_bc = 'p' ) 	
      ) 
	  and score_ab >=6;", stringsAsFactors=FALSE)

triplet_motifs_costanzo <- as.data.frame ( triplet_motifs_costanzo )

cw <- draw_triplet_motif_network  ( triplet_motifs_costanzo, 'essential overexpression' ) 

cw <- add_node_attributes(cw, gene_names , "oln_id")

cw <- add_node_attributes ( cw, enriched_functions, "Node.label.ORF")

displayGraph(cw)

triplet_motif_network_display_style(cw) 

redraw (cw)

current_example_dir <- file.path( results_directory, "Achilles_heel/Essential and toxic upon overexpression")

create_directory_if_not_exists( current_example_dir) 

saveImage ( cw, file.name= file.path( current_example_dir, "Essential and toxic upon overexpression"), image.type='pdf')

```



Periodically expressed and toxic upon overexpression
```{r}

triplet_motifs_costanzo <- sqldf( "select distinct oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
									from densely_annotated_triplet_motif
									where ( ( type_ac = 'p' and type_bc = 'p' )
									or  ( type_ac = 'tu' and type_bc = 'tu' ) 
									or  ( type_ac = 'ku' and type_bc = 'ku' ) 
									or  ( type_ac = 'p' and type_bc = 'ku' ) 
									or  ( type_ac = 'p' and type_bc = 'td' ) 
									or  ( type_ac = 'p' and type_bc = 'kd' ) 
									or  ( type_ac = 'ku' and type_bc = 'p' ) 
									or  ( type_ac = 'td' and type_bc = 'p' ) 
									or  ( type_ac = 'kd' and type_bc = 'p' ) 	
									) 
									and periodically_expressed_a = 1
									and periodically_expressed_b = 1
									and periodically_expressed_c = 1

									
									and overexpression_toxic_a = 1
									and overexpression_toxic_b = 1
									and overexpression_toxic_c = 1

									except 
									
									select oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
									from densely_annotated_triplet_motif
									where ( ( type_ac = 'p' and type_bc = 'p' )
									or  ( type_ac = 'tu' and type_bc = 'tu' ) 
									or  ( type_ac = 'ku' and type_bc = 'ku' ) 
									or  ( type_ac = 'p' and type_bc = 'ku' ) 
									or  ( type_ac = 'p' and type_bc = 'td' ) 
									or  ( type_ac = 'p' and type_bc = 'kd' ) 
									or  ( type_ac = 'ku' and type_bc = 'p' ) 
									or  ( type_ac = 'td' and type_bc = 'p' ) 
									or  ( type_ac = 'kd' and type_bc = 'p' ) 	
									) 
									and score_ab >=6;", stringsAsFactors=FALSE)

triplet_motifs_costanzo <- as.data.frame ( triplet_motifs_costanzo )

cw <- draw_triplet_motif_network  ( triplet_motifs_costanzo, 'periodically expressed and toxic upon overexpression' ) 

cw <- add_node_attributes(cw, gene_names , "oln_id")

cw <- add_node_attributes ( cw, enriched_functions, "Node.label.ORF")

displayGraph(cw)

triplet_motif_network_display_style(cw) 

redraw (cw)

current_example_dir <- file.path( results_directory, "Achilles_heel/Periodically expressed and toxic upon overexpression")

create_directory_if_not_exists( current_example_dir) 

saveImage ( cw, file.name= file.path( current_example_dir, "Periodically expressed and toxic upon overexpression"),
			image.type='pdf')

```
